---
title: "HW3"
author: "Andrew Li"
date: "10/15/2022"
output: html_document
---

```{r setup, include=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

### Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays.

```{r}
delay_airports = flights %>%
  group_by(dest) %>%
  summarise(average_arr_delay = mean(arr_delay, na.rm=T),
            average_dep_delay = mean(dep_delay, na.rm=T)) %>%
  right_join(airports, c("dest" = "faa"))

delay_airports %>%
  semi_join(flights) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point(aes(size = average_arr_delay, color=average_dep_delay)) +
    scale_size_continuous(range=c(1.5, 3)) +
    coord_quickmap()
```

### Add the location of the origin and destination (i.e. the lat and lon) to flights
```{r}
flights_location = flights %>%
  left_join(select(airports, lat, lon, faa), by=c("dest" = "faa")) %>%
  left_join(select(airports, lat, lon, faa), by=c("origin" = "faa"))
flights_location
```

### Is there a relationship between the age of a plane and its delays?
```{r}
age_flights = planes %>%
  mutate(age = 2013 - year) %>%
  select(age, tailnum) %>%
  right_join(flights, by="tailnum") %>%
  group_by(age) %>%
  summarise(average_dep_delay = mean(dep_delay, na.rm=T),
            average_arr_delay = mean(arr_delay, na.rm=T))
age_flights %>%
  ggplot(aes(x = age, y = average_dep_delay)) +
  geom_point()
age_flights %>%
  ggplot(aes(x = age, y = average_arr_delay)) +
  geom_point()
```

We can see that there is no clear relationship between the age of the plane and
the delays that it suffers.

